Neural networks for solving regression and classification problems

### 2022-11-07 doc/paper.tex
Add implementation part

We implement the FFNN as a class, using NumPy's many y

We set the bias to 0.1 as recommended in Goodfellow et Al. \cite[189]{gbc}.

@@

@@

To gain insight into how the three different regression methods work, we experiment with synthetic data generated by the Franke function.

>>>>

We implement the FFNN as a class, using NumPy's many matrix functions. In the instantiation of the class, one is able to specify an arbitrary architecture, and choose activation functions for the output and the hidden layer. The cost function can also be specified, and this, along with the choice of output function, allows the network to be used for regression, binary classification and multiclass classification. By specifying no hidden layers in the architecture, the model can be used for linear and logistic regression as well. Because of this, no explicit implementation of linear and logistic regression has been made, which means that almost all relevant code is contained in \texttt{src/FFNN.py} and \texttt{src/Schedulers.py}. When instatiating the model, we set the weights to normal distributions with mean zero and variance one. We set the bias to $0.1$ as recommended in Goodfellow et Al. \cite[189]{gbc}.

The feedforward part is implemented as a simple matrix vector multiplication, followed by an elementwise application of the chosen activation function. For processing batches of inputs, the same multiplication code is used, but this time the input is the design matrix instead of a single row. Each hidden layer will now contain matrices themselves, consisting of a number of rows equivalent to the batch size and a number of columns equal to the number of nodes in this layer.

The backpropagation is implemented by differentiating all the functions declared when the class is instatiated, and following the algorithm laid out in Hjort-Jensens lectures \cite{morten}. For batch backpropagation, we accumulate the gradient. In practice this means that the gradient for the weights, normally a matrix the same size as the relevant weight matrix, is now one matrix per element in our batch (in practice implemented as a NumPy array of three dimensions). At the end of the batch, we sum all the gradients for each weight matrix together and subtract this from the corresponding weight matrix.

Training a model is implemented as repeated calls to feedforward and backpropagation, once per batch per epoch. During training, one is able to specify which scheduler to use. These are implemented as a series of classes all inheriting from a base class, and are all implemented following Hjort-Jensens lectures \cite{mortensched}. For finding the optimal parameters, we implement our own gridsearch which finds the lowest error among combinations of $\lambda$, $\eta$, and parameters used in for the scheduling.

@@

\subsection{Different schedulers used with linear regression}

\subsection{Neural Network for regression}

For the organic terrain data used in our previous project, we found that our neural net performed slightly better, gaining an MSE of NUMBER, which was about PERCENTAGE better than our best polynomial fit. However, looking at our prediction visually, and also comparing the MSE to the one gained on the Franke Function, we see that we are still lacking. For terrain data like this, which contain a lot of spatial information, we believe that Convolutional Neural Networks could be a better fit.

\subsection{Neural Network for binary and multiclass classification}

To test our networks ability to classify data, we trained it on many common datasets used in the development of neural networks. The datasets were the Wisconsin Breast Cancer dataset and the 8x8 MNIST dataset, as well as other datasets\footnote{Sonar dataset, House dataset}. We found good results on all datasets achieving a test accuracy of over 97\% on all

@@

Although our neural network performed well, we also found very similar results with logistic regression, at a much lower computational cost. This implies that our classification datasets were perhaps too simple, and that using Neural Networks was perhaps not needed to achieve good results.
